Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-19 paper.tex
Add wake figures for Re_D = 1 x 10^6
Add two paragraphs to wake measurements section based on JoT results

\begin{figure}[ht]
\caption{Airfoil lift to drag ratio as a function of Reynolds number, from 
\cite{McMasters1980}.}
\label{fig:McMasters}
\end{figure}

@@

\todo[inline]{Put wake characteristics here. Maybe create difference plots to
show absolute differences, or RMS, or something}

\todo[inline]{Plot asymptotic behavior for a bunch of locations all on the same
plot.}

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=0.7\textwidth]{figures/McMasters-Henderson-1980}
\caption{Airfoil lift to drag ratio as a function of Reynolds number, from 
\cite{McMasters1980}.}
\label{fig:McMasters}
\end{figure}

@@

The wake of this turbine at $x/D=1$, $\lambda=1.9$, $Re_D = 1.0 \times 10^6$ was
described thoroughly in \cite{Bachant2015-JoT}. Similar data were taken for the
experiment here, the results for the mean velocity field and turbulence kinetic
energy are shown in Figure~\ref{fig:meancontquiv} and Figure~\ref{fig:kcont},
respectively. With respect to the mean velocity field, we see asymmetry and a
mean vortex structure created by the blade tip vortex shedding. The effects of
the tip vortices are also seen in the turbulence kinetic energy measurements,
along with turbulence generated by the blades undergoing dynamic stall on the
$-y$ side of the turbine.

These same wake maps were taken for $Re_D = 0.4 \time 10^6$, $0.6 \times 10^6$,
$0.8 \times 10^6$, and $1.2 \times 10^6$. Qualitatively, these look strikingly
similar, so they have not been plotted here. We will instead compare and
contrast the wake behavior by examining spectra and wake transport terms in the
equations that govern the downstream evolution.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth]{figures/meancontquiv_10}
\caption{Mean velocity field at $x/D=1$, $\lambda=1.9$, and $Re_D=1.0 \times 10^6$.}
\label{fig:meancontquiv}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth]{figures/k_contours_10}
\caption{Turbulence kinetic energy at $x/D=1$, $\lambda=1.9$, and 
$Re_D=1.0 \times 10^6$.}
\label{fig:kcont}
\end{figure}
